Supplementary file 1: Preregistered analysis

### 2025-04-07 preregistration_code.Rmd
include code in prereg

---
title: "Supplementary file 1: Preregistered analysis"
author: "Abigail Edwards and Mikko Arvas"
date: "`r Sys.time()`"
output:
  html_document:
    toc: yes
    theme: united
  pdf_document:
    toc: yes
---

TODO:
 -remove superfluous outputs
 -check discussion with Lauri, was there anything else to do?
 -check model saving
 -fill out the preregistration form

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
library(worcs)
library(tidyverse)
library(gtsummary)
library(likert)
library(here)
library(corrplot)
library(ggstats)
library(lavaan)
library(lavaanPlot)
#library(semPlot) # update plots to semPlot later
#library(blavaan) # could not get it to work with this model and synthetic data
#library(tidySEM) # https://github.com/yrosseel/lavaan/issues/359 lavaan does not work if tidySEM is loaded.
```

@@

Items
<table>
<tr>
<td></td>
<td> Psychological ownership</td>
</tr>
<tr>
<td>po01</td>
<td>
1. I feel a very high degree of personal ownership of donating blood.
</td>
</tr>
<tr>
<td>po02</td>
<td>
2. I feel like donating blood belongs to me.
</td> </tr>
<tr>
<td>po03</td> <td>
3. I feel like I own donating blood.
</td> </tr>
<tr> <td></td>

<td>
Self-identity
</td> </tr>
<tr>
<td>si01</td>
<td>
1. Donating blood is important to me.
</td> <tr>
<td>si02</td> <td>
2. I am like the kind of person who donates blood.
</td> </tr>
<tr> <td>si03</td> 
<td>
3. Donating blood is an important part of who I am.
</td> </tr>
<tr> <td></td>

<td>
Intention
</td></tr>
<tr><td>it01</td>
<td>
1. I would like to donate blood in the future.
</td>   </tr>
<tr><td>it02</td>
<td>
2. I intend to donate blood in the future.
</td> </tr>
<tr><td>it03</td>

<td>
3. I intend to make more than just a one-off blood donation.
</td></tr>
<tr><td></td>
<td>
Intention to donate for emergency
</td></tr>
<tr><td>ie01</td>
<td>
1. I would be willing to donate blood if I received an urgent callout from the Finnish Red Cross Blood Service.
</td></tr>
<tr><td></td> 
<td>
Antecedents of psychological ownership
</td></tr>
<tr><td></td>

<td>
Control
</td></tr>
<tr><td>ac01</td>
<td>
1. I have influence over the things that affect me while donating blood.
</td></tr>
<tr><td>ac02</td>
<td>
2. I control the location and scheduling for donating blood.
</td></tr>
<tr><td>ac03</td>
<td>
3. I influence decisions related to my blood donation.
</td></tr>
<tr><td>ac04</td>
<td>
4. In general, I have control over donating blood.
</td></tr>
<tr><td></td>
<td>
Intimate knowledge
</td></tr>
<tr><td>ai01</td>

<td>
1. I am intimately familiar with what is going on with regard to donating blood.
</td></tr>
<tr><td>ai02</td>
<td>
2. I have a depth of knowledge as it relates to donating blood.
</td></tr>
<tr><td>ai03</td>
<td>
3. I have a comprehensive understanding of donating blood.
</td></tr>
<tr><td>ai04</td>
<td>
4. I have a broad understanding of donating blood.
</td></tr>
<tr><td></td>

<td>
Self-Investment
</td></tr>
<tr><td>iv01</td>
<td>
1.	I have invested a major part of myself into donating blood.
</td></tr>
<tr><td>iv02</td>
<td>
2. I have invested a significant amount of my time into donating blood.
</td></tr>
<tr><td>iv03</td>
<td>
3. Overall, I invested a lot into donating blood.
</td></tr>
<tr><td></td>

<td>
Blood donation history
</td></tr>
<tr><td>bd01</td>
<td>
1. Do you believe that you are currently eligible to donate blood [yes, no, unsure]
</td></tr>
<tr><td>bd02</td>
<td>
2. How many times in total have you donated blood at the Finnish Red Cross Blood Service Finland? [select number]
</td></tr>
<tr><td>bd03</td>
<td>
3. How many times in the last two years have you donated at the Finnish Red Cross Blood Service? [select number]
</td></tr>
<tr><td>bd04</td>
<td>
4. When did you last attend a Finnish Red Cross blood donation centre with the intention of donating blood? [select date]
</td></tr>
<tr><td></td>

<td>
Demographics
</td></tr>
<tr><td>de01</td>
<td>1. What is your gender? [man, woman, non-binary, prefer to not disclose, prefer to self-describe (open response)]
</td></tr>
<tr><td>de02</td>
<td>
2. How old are you today? [select number]
</td></tr>
</table>

@@

  ) %>%
  add_n()  # add column with total number of non-missing observations
table1
```

@@

```{r , fig.height=20}
lavaanPlot(
  fit.po01.cfa,
   edge_options = list(color = "grey"),
  coefs = TRUE,
  graph_options = list(rankdir = "LR")
           )
```

@@

  )
```

```{r}
# Same with standardised coefficients
lavaanPlot(
  model = fit.po02ss, 
   labels = labelsforplottingnull,
  node_options = list(shape = "box", fontname = "Helvetica"), 
  edge_options = list(color = "grey"), 
  coefs = TRUE, 
  stand = TRUE,
  sig=0.001
  )
```

@@

  )
```

```{r}
# Same with standardised coefficients
lavaanPlot(
  model = fit.po02, 
   labels = labelsforplotting,
  node_options = list(shape = "box", fontname = "Helvetica"), 
  edge_options = list(color = "grey"), 
  coefs = TRUE, 
  stand = TRUE,
  sig=0.001
  )
```

@@

```{r}
lavaanPlot(
  model = fit.po03ss, 
   labels = labelsforplottingnull,
  node_options = list(shape = "box", fontname = "Helvetica"), 
  edge_options = list(color = "grey"), 
  coefs = TRUE, 
  stand = TRUE,
  sig=0.001
  )

@@

```{r}
lavaanPlot(
  model = fit.po03, 
   labels = labelsforplotting,
  node_options = list(shape = "box", fontname = "Helvetica"), 
  edge_options = list(color = "grey"), 
  coefs = TRUE, 
  stand = TRUE,
  sig=0.001
  )

@@

```{r}
if (fitmodels) {
  save(models,file=here(str_replace(str_c("results/",datafile),"\\.data\\.",".models.")))
}
```

>>>>

---
title: "Supplementary file 1: Preregistered analysis"
author: "Abigail Edwards, Lauri Hietajärvi and Mikko Arvas"
date: "`r Sys.time()`"
output:
  pdf_document:
    toc: yes

always_allow_html: true
---

TODO:

 -remove superfluous outputs

 -check discussion with Lauri, was there anything else to do?

 -check model saving

 -fill out the preregistration form

 -are Abigail's sum score coefficients bootstrapped?

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
library(worcs)
library(tidyverse)
library(gtsummary)
library(likert)
library(here)
library(corrplot)
library(ggstats)
library(lavaan)
library(lavaanPlot)
library(kableExtra)
#library(semPlot) # update plots to semPlot later
#library(blavaan) # could not get it to work with this model and synthetic data
#library(tidySEM) # https://github.com/yrosseel/lavaan/issues/359 lavaan does not work if tidySEM is loaded.
```

@@

@@

  ) %>%
  add_n()  # add column with total number of non-missing observations
as_kable_extra(table1, format = "latex")
```

@@

```{r , fig.height=20}
lavaanPlot(
  fit.po01.cfa,
   edge_options = list(color = "grey"),
  coefs = TRUE,
  graph_options = list(rankdir = "LR")
           ) %>% lavaanPlot::embed_plot_pdf(here("figures/cfa01.pdf"))
```

@@

  ) %>% lavaanPlot::embed_plot_pdf(here("figures/plsssem01.pdf"))
```

```{r}
# Same with standardised coefficients
lavaanPlot(
  model = fit.po02ss, 
   labels = labelsforplottingnull,
  node_options = list(shape = "box", fontname = "Helvetica"), 
  edge_options = list(color = "grey"), 
  coefs = TRUE, 
  stand = TRUE,
  sig=0.001
  ) %>% lavaanPlot::embed_plot_pdf(here("figures/plsssem02.pdf"))
```

@@

  ) %>% lavaanPlot::embed_plot_pdf(here("figures/pllvsem01.pdf"))
```

```{r}
# Same with standardised coefficients
lavaanPlot(
  model = fit.po02, 
   labels = labelsforplotting,
  node_options = list(shape = "box", fontname = "Helvetica"), 
  edge_options = list(color = "grey"), 
  coefs = TRUE, 
  stand = TRUE,
  sig=0.001
  ) %>% lavaanPlot::embed_plot_pdf(here("figures/pllssem02.pdf"))
```

@@

```{r}
lavaanPlot(
  model = fit.po03ss, 
   labels = labelsforplottingnull,
  node_options = list(shape = "box", fontname = "Helvetica"), 
  edge_options = list(color = "grey"), 
  coefs = TRUE, 
  stand = TRUE,
  sig=0.001
  ) %>% lavaanPlot::embed_plot_pdf(here("figures/plsssem03.pdf"))

@@

```{r}
lavaanPlot(
  model = fit.po03, 
   labels = labelsforplotting,
  node_options = list(shape = "box", fontname = "Helvetica"), 
  edge_options = list(color = "grey"), 
  coefs = TRUE, 
  stand = TRUE,
  sig=0.001
  ) %>% lavaanPlot::embed_plot_pdf(here("figures/pllvsem03.pdf"))

@@

```{r}
if (fitmodels) {
  save(models,file=here("prereg_models.rdata"))
}
```
